\documentclass[0-thesis.tex]{subfiles}

\begin{document}

\section{Background}
% Explain what IoT is
Internet of Things, or IoT, is the notion of connecting physical objects to the world-spanning 
Internet in order to facilitate services and communication both machine-to-human and 
machine-to-machine. By having everything connected, from everyday appliances to vehicles to 
critical parts of infrastructure, computers will be ubiquitous and the Internet of Things 
realized. The benefits from the IoT can range from quality of life services, such as controlling 
lights and thermostats from afar, to data gathering through wireless sensor networks, to 
enabling life critical operations such as monitoring a pacemaker. IoT is a broad definition 
and fits many different devices in many different environment, what they all have in common 
is that they are physical and connected devices.

In recent years the general public has become increasingly aware of digital attacks and 
intrustions affecting their day to day lives. In 2016 the DNS provider Dyn was attacked 
by a botnet consisting of heterogenous IoT devices infected by the Mirai malware. Devices 
such as printers and baby monitors were leveraged to launch an attack on Dyn's services which 
affected sites like Airbnb, Amazon, and CNN \parencite{perlroth_2016}. Cardiac devices implanted in patients were also
discovered to be unsafe, with hackers being able to deplete the batteries of pacemakers 
prematurely \parencite{hern_2017}. These cases and many others make it clear that security in IoT is a big deal.
According to Bain \& Company, the largest barrier for Internet of Things (IoT) adoptation 
is security concerns, and customers would buy an average of 70\% more IoT devices if they 
were secured \parencite{ali_bosche_ford_2018}. Despite security being today lacking in IoT, the 
field is expected to grow rapidly and an increase in unsecured devices could spell disaster.

\section{Problem Statement}
There is a need for secure software and firmware updates for IoT devices as vulnerabilities 
must be patched. For battery powered, remote IoT devices with long lifespans (exceeding five years) 
these patches must be applied over long distances and possibly unreliable communication channels.
There are non-open, proprietary solutions developed for specific devices but no open and 
interoperable standard. The IETF SUIT working group aims to define an architecture for such a 
mechanism without defining new transport or discovery mechanisms \parencite{suit}. By expanding upon the work of 
the SUIT group, a standardized update mechanism suitable for battery powered, constrained, and remote 
IoT devices can be developed.

\subsection{Problem}
The thesis project will examine the architecture proposed by SUIT in order to create and evaluate an 
updating mechanism for battery powered, constrained, and remote IoT devices with a life span 
exceeding five years. The update mechanism can be considered as two parts, communication and upgrading.
Communication will happen over unreliable channels and the payloads must arrive intact and untampered 
with. The upgrade mechanism itself must ensure integrity of the target image and safely perform the 
upgrade with a limited amount of memory. The thesis will examine the update mechanism from the viewpoint 
of IoT devices running the Contiki-NG operating system on 32-bit ARM Cortex M3 proceeeors. A suitable 
public key infrastructure developed by RISE will also be an underlying assumption for the work. The thesis 
aims to investigate the problem "How can the SUIT architecture be used to provide secure software and firmware 
update for the Internet of Things?".

\subsection{Purpose}
The purpose of the thesis project is to provide an open and interoperable software and firmware update 
mechanism that complies with the standards suggested by the IETF SUIT working group. This will aid other 
projects trying to secure their IoT devices following accepted standards.

\subsection{Goal}
The goals of the thesis are to study current solutions and then propose lightweight end-to-end protocols 
that can be used when updating IoT devices. The degree project shall deliver specifications and prototypes
of the protocols in an IoT testbed, as well as a thesis report.

\section{Methodologies}
The thesis will follow a mix of qualitative and quantitative methodologies. The SUIT group defines some 
goals or constraints a suitable updating mechanism should follow, but as their proposed architecture is 
agnostic of any particular technology these goals cannot be easily quantified. It is better to regard them 
as qualitative properties the mechanism should have. In addition to this there are some relevant measurements,
such as reliability of the communication and memory and power requirements of the updates, that can be used 
in an evaluation. The quantitative part of the evaluation will follow an objective, experimental approach, while 
the qualitative part will follow a interpretative approach.

\section{Risks, Consequences, and Ethics}
IoT devices need to be securely updated in order to fix vulnerabilities and undergo maintenance to ensure 
their future operability. Failing to do so could leave a device or network unsecured, posing a security risk. 
Furthermore the performance of the service provided by the IoT device may itself degrade. Lastly, if updates 
are not applied in a safe and secure manner, the updating mechanism itself might cause service disruptions.
These risks are serious and could pose ethical dilemmas depending on what the IoT device is used for.

\section{Scope}
The updating mechanism can be split into three rough parts: the actual updating or flipping of 
images on the device, the transportation of the new image, and managing a heterogenous network
of devices needed different updates at different times. This thesis will only look at the first 
two parts, updating a firmware image on the device and transportation of the image. The thesis 
will not be concerned about device management.

\section{Outline}
% TODO: Fix wonky formatting when beginning new lines. Better to write it into a coherent piece
Chapter two describes the theoretical background needed to understand the results of the thesis.
Chapter three describes the design of the communication protocols used in the update mechanism.
Chapter four describes how the update mechanism works and how devices can upgrade their images.
Chapter five evaluates the developed updating mechanism and presents the results.
Chapter six ends the report with a discussion about the update mechanism and its results.

\end{document}